---
title: "Mean and variance functions used to simulate Gaussian data"
author: "Zhengrong Xing, Peter Carbonetto and Matthew Stephens"
output: workflowr::wflow_html
---

## Set up environment

Load the ggplot2 and cowplot packages, and the functions definining
the mean and variances used to simulate the data.

```{r load-pkgs, message=FALSE, warning=FALSE}
library(ggplot2)
library(cowplot)
source("../code/signals.R")
```

## Generate the ground-truth signals

Here, `n` specifies the length of the signals.

```{r specify-n}
n = 1024
t = 1:n/n
```

Some code.

```{r}
mu.s = spike.f(t)
```

More code.

```{r}
pos = c(0.1, 0.13, 0.15, 0.23, 0.25, 0.4, 0.44, 0.65, 0.76, 0.78, 0.81)
hgt = 2.97/5 * c(4, 5, 3, 4, 5, 4.2, 2.1, 4.3, 3.1, 5.1, 4.2)
wth = c(0.005, 0.005, 0.006, 0.01, 0.01, 0.03, 0.01, 0.01, 0.005, 0.008, 0.005)
mu.b = rep(0, n)
for (j in 1:length(pos))
  mu.b = mu.b + hgt[j]/((1 + (abs(t - pos[j])/wth[j]))^4)

mu.dop     = dop.f(t)
mu.dop     = 3/(max(mu.dop) - min(mu.dop)) * (mu.dop - min(mu.dop))
mu.dop.var = 10 * dop.f(t)
mu.dop.var = mu.dop.var - min(mu.dop.var)

sig = ((2 * t + 0.5) * (t <= 0.15)) +
      ((-12 * (t - 0.15) + 0.8) * (t > 0.15 & t <= 0.2)) +
      0.2 * (t > 0.2 & t <= 0.5) + 
      ((6 * (t - 0.5) + 0.2) * (t > 0.5 & t <= 0.6)) +
      ((-10 * (t - 0.6) + 0.8) * (t > 0.6 & t <= 0.65)) +
      ((-0.5 * (t - 0.65) + 0.3) * (t > 0.65 & t <= 0.85)) +
      ((2 * (t - 0.85) + 0.2) * (t > 0.85))
mu.ang = 3/5 * ((5/(max(sig) - min(sig))) * sig - 1.6) - 0.0419569

heavi = 4 * sin(4 * pi * t) - sign(t - 0.3) - sign(0.72 - t)
mu.hs = heavi/sqrt(var(heavi)) * 1 * 2.99/3.366185
mu.hs = mu.hs - min(mu.hs)

pos    = c(0.1, 0.13, 0.15, 0.23, 0.25, 0.4, 0.44, 0.65, 0.76, 0.78, 0.81)
hgt    = 2.88/5 * c(4, (-5), 3, (-4), 5, (-4.2), 2.1, 4.3, (-3.1), 2.1, (-4.2))
mu.blk = rep(0, n)
for (j in 1:length(pos))
  mu.blk = mu.blk + (1 + sign(t - pos[j])) * (hgt[j]/2)

mu.cblk = mu.blk
mu.cblk[mu.cblk < 0] = 0
```

Define the Blip mean function.

```{r define-blip}
mu.blip = (0.32 + 0.6 * t +
           0.3 * exp(-100 * (t - 0.3)^2)) * (t >= 0 & t <= 0.8) +
  (-0.28 + 0.6 * t + 0.3 * exp(-100 * (t - 1.3)^2)) * (t > 0.8 & t <= 1)
```
  
Define the Corner mean function.

```{r define-corner}
mu.cor = 623.87 * t^3 * (1 - 2 * t) * (t >= 0 & t <= 0.5) +
         187.161 * (0.125 - t^3) * t^4 * (t > 0.5 & t <= 0.8) +
         3708.470441 * (t - 1)^3 * (t > 0.8 & t <= 1)
mu.cor = (0.6/(max(mu.cor) - min(mu.cor))) * mu.cor
mu.cor = mu.cor - min(mu.cor) + 0.2
```

Define the rest of the mean functions.

```{r define-mean}
mu.sp   = (1 + mu.s)/5
mu.bump = (1 + mu.b)/5
mu.blk  = 0.2 + 0.6 * (mu.blk - min(mu.blk))/max(mu.blk - min(mu.blk))
mu.ang  = (1 + mu.ang)/5
mu.dop  = (1 + mu.dop)/5
```

Define the variance functions.

```{r define-variance}
var1 = rep(1, n)
var2 = (1e-02 + 4 * (exp(-550 * (t - 0.2)^2) +
                     exp(-200 * (t - 0.5)^2) +
                     exp(-950 * (t - 0.8)^2)))
var3 = (1e-02 + 2 * mu.dop.var)
var4 = 1e-02 + mu.b
var5 = 1e-02 + 1 * (mu.cblk - min(mu.cblk))/max(mu.cblk)
var1 = var1/2
var2 = var2/max(var2)
var3 = var3/max(var3)
var4 = var4/max(var4)
var5 = var5/max(var5)
```

## Plot the signal means

These plots show each of the mean functions used to generate the
simulated data sets.

```{r plot-mean-functions, fig.height=10, fig.width=6}
plot_grid(qplot(t,mu.sp,  geom = "line",xlab = "",ylab = "",main = "Spikes"),
          qplot(t,mu.bump,geom = "line",xlab = "",ylab = "",main = "Bumps"),
          qplot(t,mu.blk, geom = "line",xlab = "",ylab = "",main = "Blocks"),
          qplot(t,mu.ang, geom = "line",xlab = "",ylab = "",main = "Angles"))
# plot(t,mu.dop,xlab = "",ylab = "",type = "l",main = "Doppler mean function")
# plot(t,mu.blip,xlab = "",ylab = "",type = "l",main = "Blip mean function")
# plot(t,mu.cor,xlab = "",ylab = "",type = "l",main = "Corner mean function")
```

## Plot the signal variances

These are rescaled in the simulations to achieve the desired signal
to noise ratios.

```{r plot-variance-functions}
plot(t,var1,xlab = "",ylab = "",ylim = c(0,1),type = "l",
     main = "Constant variance function")
plot(t,var2,xlab = "",ylab = "",type = "l",
     main = "Triple exponential variance function")
plot(t,var3,xlab = "",ylab = "",type = "l",main = "Doppler variance function")
plot(t,var4,xlab = "",ylab = "",type = "l",main = "Bumps variance function")
plot(t,var5,xlab = "",ylab = "",type = "l",main = "Clipped variance function")
```
