---
title: "Motorcycle Acceleration example"
author: "Zhengrong Xing, Peter Carbonetto and Matthew Stephens"
output: workflowr::wflow_html
---

This is an illustration of "smoothing via adaptive shrinkage" (SMASH)
applied to the Motorcycle Accident data. This implements the
"illustrative application" presented in Sec. 5.1 of the manuscript.

```{r knitr-opts, include=FALSE}
knitr::opts_chunk$set(comment = "#",collapse = TRUE,fig.align = "center")
```

Initial setup instructions
--------------------------

To run this example on your own computer, please follow these setup
instructions. These instructions assume you already have R and/or
RStudio installed on your computer.

Download or clone the [git repository][smash-github] on your computer.

Launch R, and change the working directory to be the "analysis" folder
inside your local copy of the git repository.

Install the devtools, wavethresh and EbayesThresh packages used here
and in the code below:

```{r install-pkgs-1, eval=FALSE}
install.packages(c("devtools","wavethresh","EbayesThresh"))
```

Finally, install the smashr package from GitHub:

```{r install-pkgs-2, eval=FALSE}
devtools::install_github("stephenslab/smashr")
```

See the "Session Info" at the bottom for the versions of the software
and R packages that were used to generate the results shown below.

Set up R environment
--------------------

Load the MASS, lattice wavethresh, EbayesThresh and smashr
packages. The MASS package is loaded only for the Motorcycle Accident
data. Some additional functions are defined in file
`motorcycle.functions.R`.

```{r load-pkgs, message=FALSE}
library(MASS)
library(lattice)
library(smashr)
library(wavethresh)
library(EbayesThresh)
source("../code/motorcycle.functions.R")
```

Note that the MASS and lattice packages are included in most standard
R installations, so you probably don't need to install these packages
separately.

Prepare data for SMASH
----------------------

Load the motorcycle data from the MASS package, and order the data
points by time.

```{r prepare-data}
data(mcycle)
x.ini.mc <- sort(mcycle$times)
y.ini.mc <- mcycle$accel[order(mcycle$times)]
```

Run SMASH
---------

Apply SMASH to the Motorcycle Accident data set.

```{r run-smash}
res.mc <- smash.wrapper(x.ini.mc,y.ini.mc)
```

Summarize results of SMASH analysis
-----------------------------------

Create a plot showing the Motorcycle Accident data and the smash
estimates (with the dashed red lines showing the confidence
intervals).

```{r plot-smash-estimates, fig.height=5, fig.width=7}
plot(res.mc$x,res.mc$mu.est,type = "l",
     ylim = c(min(res.mc$y - 2 * sqrt(res.mc$var.est)),
              max(res.mc$y + 2 * sqrt(res.mc$var.est))),
     xlab = "time (ms)", ylab = "acceleration (g)",lwd = 2,
	 col = "darkorange",xlim = c(0,60),xaxp = c(0,60,6))
lines(res.mc$x, res.mc$mu.est + 2*sqrt(res.mc$var.est),lty = 5,
	 lwd = 2,col = "dodgerblue")
lines(res.mc$x,res.mc$mu.est - 2*sqrt(res.mc$var.est),
      lty = 5,lwd = 2,col = "dodgerblue")
points(res.mc$x,res.mc$y,pch = 1,cex = 1,col = "black")
```

SMASH, homoskedastic vs. heteroskedastic
----------------------------------------

Apply SMASH, this time assuming equal variances, to the Motorcycle
Accident data set:

```{r run-smash-homo}
res.cons.mc <- smash.cons.wrapper(x.ini.mc,y.ini.mc)
```

In this second plot, we compare the mean estimate provided by SMASH
(with heteroskedastic variances; orange line) against homoskedastic
SMASH (dotted, light blue line).

```{r plot-homo-smash-estimates, fig.height=5, fig.width=7}
plot(res.mc$x,res.mc$mu.est,type = "l",
     ylim = c(min(res.mc$y - 2 * sqrt(res.mc$var.est)),
              max(res.mc$y + 2 * sqrt(res.mc$var.est))),
	 xlab = "time (ms)",ylab = "acceleration (g)",lwd = 2,
	 col = "darkorange",xlim = c(0,60),xaxp = c(0,60,6))
lines(res.cons.mc$x,res.cons.mc$mu.est,lwd = 2,lty = "dotted",
      col = "dodgerblue")
points(res.mc$x,res.mc$y,pch = 1,cex = 0.8,col = "black")
```

While the estimates are similar, heteroskedastic SMASH yields a
noticeably smoother curve.

Apply TI thresholding to the Motorcycle Accident data
-----------------------------------------------------

Apply TI thresholding to the Motorcycle Accident data set. In this
first run, the variance is assumed to be constant.

```{r run-tithresh}
res.ti.cons.mc <- tithresh.cons.wrapper(x.ini.mc,y.ini.mc)
```

Apply TI thresholding to the Motorcycle Accident data, this time using
the variances estimated using the "median absolute deviation", or
RMAD, method.

```{r run-tithresh-rmad}
res.ti.rmad.mc <- tithresh.rmad.wrapper(x.ini.mc,y.ini.mc)
```

Apply TI thresholding to the Motorcycle Accident data, this time using
the variances estimated by SMASH.

```{r run-tithresh-with-smash-var}
res.ti.mc <- tithresh.wrapper(x.ini.mc,y.ini.mc)
```

Compare SMASH vs. TI thresholding
---------------------------------

In this next plot, we compare the SMASH estimates with heteroskedastic
variances (the same orange line as above) against the the mean estimates
obtained by TI thresholding with constant variance (solid dark blue
line), TI thresholding with RMAD variance estimates (solid light blue
line), and TI thresholding when the variances have been estimated by
SMASH (dotted green line).

```{r plot-ti-thresh-estimates, fig.height=5, fig.width=7}
plot(res.mc$x,res.mc$mu.est,type = "l",
     ylim = c(min(res.mc$y - 2 * sqrt(res.mc$var.est)),
              max(res.mc$y + 2 * sqrt(res.mc$var.est))),
	 xlab = "time (ms)",ylab = "acceleration (g)",lwd = 2,
	 col = "darkorange",xlim = c(0,60),xaxp = c(0,60,6))
lines(res.ti.cons.mc$x,res.ti.cons.mc$mu.est,lwd = 2,lty = "solid",
	 col = "darkblue")
lines(res.ti.rmad.mc$x,res.ti.rmad.mc$mu.est,lwd = 2,lty = "solid",
      col = "dodgerblue")
lines(res.ti.mc$x,res.ti.mc$mu.est,lwd = 2,col = "limegreen",lty = "dotted")
points(res.mc$x,res.mc$y,pch = 1,cex = 0.8,col = "black")
```

The TI thresholding estimate, like the SMASH estimate with
homoskedastic variances, shows notable artifacts. When TI thresholding
estimates the variance using RMAD, or when it is provided with the
SMASH variance estimate, the mean signal is substantially smoother.

[smash-github]: https://github.com/stephenslab/smash-paper
