---
title: "Motorcycle Acceleration example"
author: "Zhengrong Xing, Peter Carbonetto and Matthew Stephens"
output: workflowr::wflow_html
---

This is an illustration of "smoothing via adaptive shrinkage" (SMASH)
applied to the Motorcycle Accident data. This implements the
"illustrative application" presented in Sec. 5.1 of the manuscript.

```{r knitr-opts, include=FALSE}
knitr::opts_chunk$set(comment = "#",collapse = TRUE,fig.align = "center")
```

Initial setup instructions
--------------------------

To run this example on your own computer, please follow these setup
instructions. These instructions assume you already have R and/or
RStudio installed on your computer.

Download or clone the [git repository][smash-github] on your computer.

Launch R, and change the working directory to be the "analysis" folder
inside your local copy of the git repository.

Install the devtools, wavethresh and EbayesThresh packages used here
and in the code below:

```{r install-pkgs-1, eval=FALSE}
install.packages(c("devtools","wavethresh","EbayesThresh"))
```

Finally, install the ashr and smashr packages from GitHub:

```{r install-pkgs-2, eval=FALSE}
library(devtools)
install_github("stephens999/ashr",upgrade_dependencies = FALSE)
install_github("stephenslab/smashr",upgrade_dependencies = FALSE)
```

See the "Session Info" at the bottom for the versions of the software
and R packages that were used to generate the results shown below.

Set up R environment
--------------------

Load the MASS, wavethresh, EbayesThresh and smashr packages. The MASS
package is loaded only for the Motorcycle Accident data. Some
additional functions are defined in `functions.motorcycle.R`.

```{r load-pkgs, message=FALSE}
library(MASS)
library(lattice)
library(smashr)
library(wavethresh)
library(EbayesThresh)
source("../code/motorcycle.functions.R")
```

Note that the MASS and lattice packages are included in most standard
R installations, so you probably don't need to install these packages
separately.

Prepare data for SMASH
----------------------

Load the motorcycle data from the MASS package, and order the data
points by time.

```{r prepare-data}
data(mcycle)
x.ini.mc <- sort(mcycle$times)
y.ini.mc <- mcycle$accel[order(mcycle$times)]
```

Run SMASH
---------

Apply SMASH to the Motorcycle Accident data set.

```{r run-smash}
res.mc <- smash.wrapper(x.ini.mc,y.ini.mc)
```

Summarize results of SMASH analysis
-----------------------------------

Create a plot showing the Motorcycle Accident data and the smash
estimates (with the dashed red lines showing the confidence
intervals).

```{r plot-smash-estimates, fig.height=5, fig.width=7}
plot(res.mc$x,res.mc$mu.est,type = "l",
     ylim = c(min(res.mc$y - 2 * sqrt(res.mc$var.est)),
              max(res.mc$y + 2 * sqrt(res.mc$var.est))),
     xlab = "time (ms)", ylab = "acceleration (g)",lwd = 2,
	 col = "darkorange",xlim = c(0,60),xaxp = c(0,60,6))
lines(res.mc$x, res.mc$mu.est + 2*sqrt(res.mc$var.est),lty = 5,
	 lwd = 2,col = "dodgerblue")
lines(res.mc$x,res.mc$mu.est - 2*sqrt(res.mc$var.est),
      lty = 5,lwd = 2,col = "dodgerblue")
points(res.mc$x,res.mc$y,pch = 1,cex = 1,col = "black")
```

Apply SMASH again, this time assuming equal variances
-----------------------------------------------------

Apply SMASH (assuming equal variances) to the Motorcycle Accident data
set.

```{r run-smash-homo}
res.cons.mc <- smash.cons.wrapper(x.ini.mc,y.ini.mc)
```

Apply TI thresholding to the Motorcycle Accident data
-----------------------------------------------------

Apply TI thresholding to the Motorcycle Accident data set.

```{r run-tithresh}
res.ti.cons.mc <- tithresh.cons.wrapper(x.ini.mc,y.ini.mc)
```

Apply TI thresholding to the Motorcycle Accident data, this time using
the variances estimated by SMASH.

```{r run-tithresh-with-smash-var}
res.ti.mc <- tithresh.wrapper(x.ini.mc,y.ini.mc)
```

Compare results from all methods
--------------------------------

In this second plot, we compare the mean estimate provided by SMASH
(with heteroskedastic variances; orange line) against homoskedastic
SMASH (dotted magenta line), TI thresholding (dark blue line), and TI
thresholding when the variances have been estimated by SMASH (dotted
green line).

```{r plot-all-estimates, fig.height=5, fig.width=7}
plot(res.mc$x,res.mc$mu.est,type = "l",
     ylim = c(min(res.mc$y - 2 * sqrt(res.mc$var.est)),
              max(res.mc$y + 2 * sqrt(res.mc$var.est))),
	 xlab = "time (ms)",ylab = "acceleration (g)",lwd = 2,
	 col = "darkorange",xlim = c(0,60),xaxp = c(0,60,6))
lines(res.cons.mc$x,res.cons.mc$mu.est,lwd = 2,lty = "dotted",col = "magenta")
lines(res.ti.cons.mc$x,res.ti.cons.mc$mu.est,lwd = 2,lty = "solid",
      col = "darkblue")
lines(res.ti.mc$x,res.ti.mc$mu.est,lwd = 2,col = "limegreen",lty = "dotted")
points(res.mc$x,res.mc$y,pch = 1,cex = 0.8,col = "black")
```

[smash-github]: https://github.com/stephenslab/smash-paper
