---
title: "Plots and tables summarizing results of Poisson simulations"
author: "Zhengrong Xing, Peter Carbonetto and Matthew Stephens"
output: workflowr::wflow_html
---

Here we create plots and tables to compare various methods, including
SMASH, for reconstructing a spatially structured signal from
Poisson-distributed data. Similar to the Gaussian simulations, we
generated data sets using a variety of test functions and intensity
ranges. Specifically, we considered 6 test functions, rescaling the
test function so that the smallest intensity was $x$ and the largest
intensity was $y$, with $(x,y)$ set to either $(1/100, 3)$, $(1/8, 8)$
or $(1/128, 128)$.

For each combination of test function and intensity range, we
simulated 100 data sets. In the plots and tables below, we summarize
the error (MISE) in the estimates computed in the 100 data sets from
each simulation setting.

The plots for the "Bursts" simulations shown below were also included
in the manuscript.

```{r knitr-opts, include=FALSE}
knitr::opts_chunk$set(comment = "#",collapse = TRUE,fig.align = "center",
                      results = "hold")
```

Analysis settings
-----------------

We will view the results from these methods:

```{r selected-methods}
methods <- c("ash","BMSM","haarfisz_R")
```

These variables specify the row and column names for the tables:

```{r table-row-and-col-names}
```

These are settings used in plotting the test functions:

```{r plot-settings}
n <- 1024
t <- 1:n/n
```

Set up environment
------------------

Load the knitr, kableExtra, ggplot2 and cowplot packages.

```{r load-pkgs, message=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
library(ggplot2)
library(cowplot)
```

Some of the test functions are defined in `signals.R`, so we load them
here. Some additional functions are defined in file
`poisson.functions.R`.

```{r load-functions}
source("../code/poisson.functions.R")
source("../code/signals.R")
```

Load results
------------

Load the results of the simulation experiments.

```{r load-results}
load("../output/pois.RData")
```

Spikes data
-----------

This is the function used to simulate the "Spikes" data sets at
different ranges of intensities:

```{r plot-spikes-function, fig.height=4, fig.width=8}
mu.s <- spike.f(t)
plot(t,mu.s,xlab = "",ylab = "",type = "l",lwd = 2,col = "darkorange")
```

This table summarizes the results from the Spikes simulations:

```{r spikes-table, results="asis"}
mise.s.table <- cbind(mise.s.1[methods],
                      mise.s.8[methods],
                      mise.s.128[methods])
create.results.table(mise.s.table)
```

Each column shows the results at a different range of intensities.
The individual table entries give the average error (MISE) in the
estimates, in which the average is taken over the 100 data sets
simulated at the given range of intensities.

The combined violin-boxplots provide a more detailed summary of
the same results:

```{r spikes-violin-plots, fig.height=3.5, fig.width=10}
m                  <- length(mise.ash.s.1)
method.labels      <- c("Haar-Fisz","BMSM","SMASH")
mise.hf.ti.r.s.1   <- colMeans(rbind(mise.hf.ti.r.4.s.1,
                                     mise.hf.ti.r.5.s.1,
                                     mise.hf.ti.r.6.s.1,
	  		                         mise.hf.ti.r.7.s.1))
mise.hf.ti.r.s.8   <- colMeans(rbind(mise.hf.ti.r.4.s.8,
                                     mise.hf.ti.r.5.s.8,
                                     mise.hf.ti.r.6.s.8,
						  	         mise.hf.ti.r.7.s.8))
mise.hf.ti.r.s.128 <- colMeans(rbind(mise.hf.ti.r.4.s.128,
									 mise.hf.ti.r.5.s.128,
                                     mise.hf.ti.r.6.s.128,
									 mise.hf.ti.r.7.s.128))
pdat1 <- data.frame(method = factor(rep(method.labels,each = m),method.labels),
                    mise   = c(mise.hf.ti.r.s.1,mise.BMSM.s.1,mise.ash.s.1))
pdat8 <- data.frame(method = factor(rep(method.labels,each = m),method.labels),
                    mise   = c(mise.hf.ti.r.s.8,mise.BMSM.s.8,mise.ash.s.8))
pdat128 <-
  data.frame(method = factor(rep(method.labels,each = m),method.labels),
             mise   = c(mise.hf.ti.r.s.128,mise.BMSM.s.128,mise.ash.s.128))
create.violin.plots(pdat1,pdat8,pdat128)
```

Angles data
-----------

This is the function used to simulate the "Angles" data sets at
different ranges of intensities:

```{r plot-angles-function, fig.height=4, fig.width=8}
mu.ang <- angles.f(t)
plot(t,mu.ang,xlab = "",ylab = "",type = "l",lwd = 2,col = "darkorange")
```

This table summarizes the results from the Angles simulations:

```{r angles-table, results="asis"}
mise.ang.table <- cbind(mise.ang.1[methods],
                        mise.ang.8[methods],
                        mise.ang.128[methods])
create.results.table(mise.ang.table)
```

Each column shows the results at a different range of intensities.
The individual table entries give the average error (MISE) in the
estimates, in which the average is taken over the 100 data sets
simulated at the given range of intensities.

The combined violin-boxplots provide a visualization of the same
results:

```{r angles-violin-plots, fig.height=3.25, fig.width=10}
mise.hf.ti.r.ang.1   <- colMeans(rbind(mise.hf.ti.r.4.ang.1,
                                       mise.hf.ti.r.5.ang.1,
                                       mise.hf.ti.r.6.ang.1,
					  				   mise.hf.ti.r.7.ang.1))
mise.hf.ti.r.ang.8   <- colMeans(rbind(mise.hf.ti.r.4.ang.8,
 									   mise.hf.ti.r.5.ang.8,
                                       mise.hf.ti.r.6.ang.8,
                                       mise.hf.ti.r.7.ang.8))
mise.hf.ti.r.ang.128 <- colMeans(rbind(mise.hf.ti.r.4.ang.128,
                                       mise.hf.ti.r.5.ang.128,
                                       mise.hf.ti.r.6.ang.128,
									   mise.hf.ti.r.7.ang.128))
pdat1 <-
  data.frame(method = factor(rep(method.labels,each = m),method.labels),
             mise   = c(mise.hf.ti.r.ang.1,mise.BMSM.ang.1,mise.ash.ang.1))
pdat8 <-
  data.frame(method = factor(rep(method.labels,each = m),method.labels),
             mise   = c(mise.hf.ti.r.ang.8,mise.BMSM.ang.8,mise.ash.ang.8))
pdat128 <-
  data.frame(method=factor(rep(method.labels,each = m),method.labels),
             mise  =c(mise.hf.ti.r.ang.128,mise.BMSM.ang.128,mise.ash.ang.128))
create.violin.plots(pdat1,pdat8,pdat128)
```

Heavisine data
--------------

This is the function used to simulate the "Heavisine" data sets at
different ranges of intensities:

```{r plot-heavisine-function, fig.height=4, fig.width=8}
heavi <- 4 * sin(4 * pi * t) - sign(t - 0.3) - sign(0.72 - t)
mu.hs <- heavi/sqrt(var(heavi)) * 1 * 2.99/3.366185
mu.hs <- mu.hs - min(mu.hs)
plot(t,mu.hs,xlab = "",ylab = "",type = "l",lwd = 2,col = "darkorange")
```

This table summarizes the results from the Heavisine simulations:

```{r heavisine-table, results="asis"}
mise.hs.table <- cbind(mise.hs.1[methods],
                       mise.hs.8[methods],
                       mise.hs.128[methods])
create.results.table(mise.hs.table)
```

Each column shows results at a different range of intensities. The
individual table entries give the average error (MISE) in the
estimates, in which the average is taken over the 100 data sets
simulated at the given range of intensities.

The combined violin-boxplots provide a visualization of the same
results:

```{r heavisine-violin-plots, fig.height=3.25, fig.width=10}
mise.hf.ti.r.hs.1   <- colMeans(rbind(mise.hf.ti.r.4.hs.1,
                                      mise.hf.ti.r.5.hs.1,
                                      mise.hf.ti.r.6.hs.1,
						  			  mise.hf.ti.r.7.hs.1))
mise.hf.ti.r.hs.8   <- colMeans(rbind(mise.hf.ti.r.4.hs.8,
                                      mise.hf.ti.r.5.hs.8,
                                      mise.hf.ti.r.6.hs.8,
							  		  mise.hf.ti.r.7.hs.8))
mise.hf.ti.r.hs.128 <- colMeans(rbind(mise.hf.ti.r.4.hs.128,
                                      mise.hf.ti.r.5.hs.128,
                                      mise.hf.ti.r.6.hs.128,
									  mise.hf.ti.r.7.hs.128))
pdat1 <-
  data.frame(method = factor(rep(method.labels,each = m),method.labels),
             mise   = c(mise.hf.ti.r.hs.1,mise.BMSM.hs.1,mise.ash.hs.1))
pdat8 <-
  data.frame(method = factor(rep(method.labels,each = m),method.labels),
             mise   = c(mise.hf.ti.r.hs.8,mise.BMSM.hs.8,mise.ash.hs.8))
pdat128 <-
  data.frame(method=factor(rep(method.labels,each = m),method.labels),
             mise  =c(mise.hf.ti.r.hs.128,mise.BMSM.hs.128,mise.ash.hs.128))
create.violin.plots(pdat1,pdat8,pdat128)
```

Bursts data
-----------

This is the function used to simulate the "Bursts" data sets at
different ranges of intensities:

```{r plot-bursts-function, fig.height=4, fig.width=8}
I_1 <- exp(-(abs(t - 0.2)/0.01)^1.2) * (t <= 0.2) +
       exp(-(abs(t - 0.2)/0.03)^1.2) * (t > 0.2)
I_2 <- exp(-(abs(t - 0.3)/0.01)^1.2) * (t <= 0.3) +
       exp(-(abs(t - 0.3)/0.03)^1.2) * (t > 0.3)
I_3 <- exp(-(abs(t - 0.4)/0.01)^1.2) * (t <= 0.4) +
       exp(-(abs(t - 0.4)/0.03)^1.2) * (t > 0.4)
mu.bur <- 2.99/4.51804 * (4 * I_1 + 3 * I_2 + 4.5 * I_3)
plot(t,mu.bur,xlab = "",ylab = "",type = "l",lwd = 2,col = "darkorange")
```

This table summarizes the results from the Bursts simulations:

```{r bursts-table, results="asis"}
mise.bur.table <- cbind(mise.bur.1[methods],
                        mise.bur.8[methods],
                        mise.bur.128[methods])
create.results.table(mise.bur.table)
```

Each column shows results at a different range of intensities. The
individual table entries give the average error (MISE) in the
estimates, in which the average is taken over the 100 data sets
simulated at the given range of intensities.

The combined violin-boxplots provide a visualization of the same
results:

```{r bursts-violin-plots, fig.height=3.25, fig.width=10}
mise.hf.ti.r.bur.1   <- colMeans(rbind(mise.hf.ti.r.4.bur.1,
                                       mise.hf.ti.r.5.bur.1,
                                       mise.hf.ti.r.6.bur.1,
						  			   mise.hf.ti.r.7.bur.1))
mise.hf.ti.r.bur.8   <- colMeans(rbind(mise.hf.ti.r.4.bur.8,
                                       mise.hf.ti.r.5.bur.8,
                                       mise.hf.ti.r.6.bur.8,
									   mise.hf.ti.r.7.bur.8))
mise.hf.ti.r.bur.128 <- colMeans(rbind(mise.hf.ti.r.4.bur.128,
                                       mise.hf.ti.r.5.bur.128,
                                       mise.hf.ti.r.6.bur.128,
									   mise.hf.ti.r.7.bur.128))
pdat1 <-
  data.frame(method = factor(rep(method.labels,each = m),method.labels),
             mise   = c(mise.hf.ti.r.bur.1,mise.BMSM.bur.1,mise.ash.bur.1))
pdat8 <-
  data.frame(method = factor(rep(method.labels,each = m),method.labels),
             mise   = c(mise.hf.ti.r.bur.8,mise.BMSM.bur.8,mise.ash.bur.8))
pdat128 <-
  data.frame(method=factor(rep(method.labels,each = m),method.labels),
             mise  =c(mise.hf.ti.r.bur.128,mise.BMSM.bur.128,mise.ash.bur.128))
create.violin.plots(pdat1,pdat8,pdat128)
```

Clipped Blocks data
-------------------

This is the function used to simulate the "Clipped Blocks" data sets at
different ranges of intensities:

```{r plot-cb-function, fig.height=4, fig.width=8}
mu.cb <- cblocks.f(t)
plot(t,mu.cb,xlab = "",ylab = "",type = "l",lwd = 2,col = "darkorange")
```

This table summarizes the results from the Clipped Blocks simulations:

```{r cb-table, results="asis"}
mise.cb.table <- cbind(mise.cb.1[methods],
                       mise.cb.8[methods],
                       mise.cb.128[methods])
create.results.table(mise.cb.table)
```

Each column shows results at a different range of intensities. The
individual table entries give the average error (MISE) in the
estimates, in which the average is taken over the 100 data sets
simulated at the given range of intensities.

The combined violin-boxplots provide a visualization of the same
results:

```{r cb-violin-plots, fig.height=3.25, fig.width=10}
mise.hf.ti.r.cb.1   <- colMeans(rbind(mise.hf.ti.r.4.cb.1,
                                      mise.hf.ti.r.5.cb.1,
                                      mise.hf.ti.r.6.cb.1,
			  						  mise.hf.ti.r.7.cb.1))
mise.hf.ti.r.cb.8   <- colMeans(rbind(mise.hf.ti.r.4.cb.8,
                                      mise.hf.ti.r.5.cb.8,
                                      mise.hf.ti.r.6.cb.8,
									  mise.hf.ti.r.7.cb.8))
mise.hf.ti.r.cb.128 <- colMeans(rbind(mise.hf.ti.r.4.cb.128,
                                      mise.hf.ti.r.5.cb.128,
                                      mise.hf.ti.r.6.cb.128,
									  mise.hf.ti.r.7.cb.128))
pdat1 <-
  data.frame(method = factor(rep(method.labels,each = m),method.labels),
             mise   = c(mise.hf.ti.r.cb.1,mise.BMSM.cb.1,mise.ash.cb.1))
pdat8 <-
  data.frame(method = factor(rep(method.labels,each = m),method.labels),
             mise   = c(mise.hf.ti.r.cb.8,mise.BMSM.cb.8,mise.ash.cb.8))
pdat128 <-
  data.frame(method=factor(rep(method.labels,each = m),method.labels),
             mise  =c(mise.hf.ti.r.cb.128,mise.BMSM.cb.128,mise.ash.cb.128))
create.violin.plots(pdat1,pdat8,pdat128)
```

Bumps data
----------

This is the function used to simulate the "Bumps" data sets at
different ranges of intensities:

```{r plot-bumps-function, fig.height=4, fig.width=8}
mu.b <- bumps.f(t)
plot(t,mu.b,xlab = "",ylab = "",type = "l",lwd = 2,col = "darkorange")
```
	 
This table summarizes the results from the Bumps simulations:

```{r bumps-table, results="asis"}
mise.b.table <- cbind(mise.b.1[methods],
                      mise.b.8[methods],
                      mise.b.128[methods])
create.results.table(mise.b.table)
```

Each column shows results at a different range of intensities. The
individual table entries give the average error (MISE) in the
estimates, in which the average is taken over the 100 data sets
simulated at the given range of intensities.

The combined violin-boxplots provide a visualization of the same
results:

```{r bumps-violin-plots, fig.height=3.25, fig.width=10}
mise.hf.ti.r.b.1   <- colMeans(rbind(mise.hf.ti.r.4.b.1,
                                     mise.hf.ti.r.5.b.1,
                                     mise.hf.ti.r.6.b.1,
                                     mise.hf.ti.r.7.b.1))
mise.hf.ti.r.b.8   <- colMeans(rbind(mise.hf.ti.r.4.b.8,
                                     mise.hf.ti.r.5.b.8,
                                     mise.hf.ti.r.6.b.8,
									 mise.hf.ti.r.7.b.8))
mise.hf.ti.r.b.128 <- colMeans(rbind(mise.hf.ti.r.4.b.128,
									 mise.hf.ti.r.5.b.128,
									 mise.hf.ti.r.6.b.128,
									 mise.hf.ti.r.7.b.128))
pdat1 <-
  data.frame(method = factor(rep(method.labels,each = m),method.labels),
             mise   = c(mise.hf.ti.r.b.1,mise.BMSM.b.1,mise.ash.b.1))
pdat8 <-
  data.frame(method = factor(rep(method.labels,each = m),method.labels),
             mise   = c(mise.hf.ti.r.b.8,mise.BMSM.b.8,mise.ash.b.8))
pdat128 <-
  data.frame(method=factor(rep(method.labels,each = m),method.labels),
             mise  =c(mise.hf.ti.r.b.128,mise.BMSM.b.128,mise.ash.b.128))
create.violin.plots(pdat1,pdat8,pdat128)
```
